\\large Taking uncertainty in word embedding bias estimation seriously \\- a  Bayesian

### 2021-08-02 presentationESSLLI21/presentationESSLLI.Rmd
Adds presentation changes

### Closer look at Gender class

\includegraphics[width=8cm]{../images/visGenderReddit.png}

## Summary of the research

-

@@

- including contrasts in Bayesian model
- downstream tasks
- applying uncertainty to WEAT metric
- testing AIT dataset

>>>>

### Closer look at Religion class

<!-- add religion class -->

## Observations

- HPDIs for dataset level coefficients around 0 (Gender class is an exception)
<!-- he impact for associated, different, human and neutral attribute is, when averaged, quite similar -->
-

@@

- Including contrasts in Bayesian model
- Downstream tasks
- Applying uncertainty to WEAT metric
- Testing AIT dataset
